Adolescent well-being in the digital age

### 2022-03-24 00-clean.Rmd
New synthetic GWP data

```{r mock-gwp-data}
gwp_mock_path <- "data-raw/gwp-MOCK.rds"
if (dir.exists("data-raw/Gallup") & !file.exists(gwp_mock_path)) {
  library(synthpop)
  gwp_syn <- gwp %>% 
    drop_na()
  gwp_syn <- syn(
    gwp_syn, 
    method = c("", "", "", "", "", "", "normrank", "normrank"),
    maxfaclevels = 168
  )
  saveRDS(gwp_syn, gwp_mock_path)
}

>>>>

```{r mock-gwp-data}
gwp_mock_path <- "data-raw/gwp-MOCK.rds"
if (dir.exists("data-raw/Gallup") & !file.exists(gwp_mock_path)) {
  library(synthpop)
  gwp_syn <- gwp %>% 
    drop_na()
  gwp_syn <- syn(
    gwp_syn, 
    method = c("", "", "", "", "", "", "normrank", "normrank"),
    maxfaclevels = 168
  )
  gwp_syn <- tibble(gwp_syn$syn)
  saveRDS(gwp_syn, gwp_mock_path)
}
